---
title: "Lab 00 - Hello IDS!"
author: "Charlie Franklin-White"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Charlie Franklin-White", "Jamie Burrell", "Dru Keiri", 
           "Sean Wang", "Annie Loi", "Duncan Hoyland"),
  github_username = c("cfranklinwhite", "jamie-burrell", "sqaurehedge34", 
                      "sw-005", "aaaannniie", "duncan-hoyland"), 
  colour = c("blue", "blue", "purple", "green", 
             "blue", "seagreen"),
  hobby = c("Poker", "Climbing", "Basketball", 
            "Gaming", "Gaming", "Rugby"),
  favourite_number = c(2, 2, 6, 8, 7, 2 )
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The bar graph is showing the favourite number of each team member against their github username. The bars are in each team members favourite colour.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Username", 
          y = "Favourite Number",
          title = "Very Useful Graph")
```

The function *labs()* lets you give labels to the axis and title the graph.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

There is so many different hobbies that the data would uninformative because many people have specific hobbies. This would make it hard to interpret and difficult to draw conclusions. 

To improve the visualisation you could group similar hobbies and restrict the choice of indviduals, e.g. 'Sports', 'Music', 'Games'.


```{r new-pie-plot}

ggplot(team_data, aes(x="", y=1, fill=hobby)) + geom_bar(stat="identity", width=1) + coord_polar("y", start=0)


```


